\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}

\title{Live monitoring of venue attendance, \today}
\author{Roar Nind Steffensen, s144107, Mads Ejdesgaard Maibohm, s144479,\\
Kasper Lederballe Sørensen, s144453}
\date{}

\begin{document}


\maketitle

\section*{Problem Description}

The problem we have recognized is that whenever you want to go out to drink, have fun, or to meet with friends, it is hard to make an informed decision about which venue to choose. When choosing a venue, you might want to know different factors, such as the number of people there, if any of your friends are present, what kind of music do the people who are currently there like, and so on and so forth. Currently, this is not possible.

\section*{Why is the problem important?}

% Det handler om tryghed. Når man går i byen/er ude vil man gerne have det sjovt, og gerne i de rammer man ønsker og med de mennesker man ønsker. Det er træls at have det træls. 


Metropolitan areas containing great venues are often filled to the brim with mediocre or sub-par venues. Selecting the right venue is a complicated problem depending on many factors. The right venue could depend on the time of day, personal preference and current occupancy. This makes this problem dauntingly difficult to solve without seeking further information about the different possibilities.

The difficulty of this problem is even higher when the desired venue is a bar or nightclub. Since the quality of bars and nightclubs are hugely dependant on the crowd it is hard to generalize from night to night how good a bar or nightclub is. While in general selecting the wrong venue or spending too long trying to select the right venue is simply a waste of time, trying to find the right nightclub can be a costly affair.
\section*{Motivation for a solution}
% This could be a short state of the state of the art paragraph describing why available ap- proaches (frameworks, theories, running systems, commercial solutions, ...) are not good enough to solve the described problem

Currently you can view which of your friends are going to which events if they have signed up on Facebook, you can track where people are using snapchat if they have it enabled, you can research about venues using Google etc., but you cannot do all of these things in one application. You cannot live monitor how many people are at a certain bar and if they like the same music you do. You cannot see if your friends' party got sidetracked and ended with them at a certain bar that you are close to.

\noindent It would be nice to have an application that allows for these sort of queries. To be able to see which bar you might want to go to depending on which people are currently there and what kind of music they are listening to. To specify a profile that defines your likings, and being able to search for venues that match those criteria with live information.




\section*{Plan for solving the problem}
%  focusing on the main idea

%Make a great app, duh!


We plan to design an application that combines technologies already used by Snapchat, Facebook and Google. Our application should be able to track the GPS location of devices and broadcast this information to other devices depending upon certain criteria such as if they are Facebook friends, if the location is a venue or some place one wants to broadcast etc. The application should be able to gather information about its users preferences towards music, beverages, hobbies etc., such that this sort of information can be used in filtering of values.


\end{document}