\subsection{Requirements}

\subsubsection{Functional Requirements}
\begin{itemize}
    \item Communication - Clients should be able to reach and interact with the server.
    
    \item Accessibility - The server, when operational, should be available to clients at all times.
    
    \item Concurrency - A large amount of clients should be able to post to and fetch data from the server concurrently.
    
    \item Fault tolerance - The server or other clients should not be affected by a failing client.
    
    \item Location Data - The client's program should be able to access the client's device location.
    
    \item Scalability - The system should be capable of maintaining a varying amount of clients.
    
    \item Groups - Users can create and manage private groups.
\end{itemize}

\subsubsection{Non-Functional Requirements}

\begin{itemize}
    \item Privacy - Location data should not be shared without consensus between involved parties.
    
    \item Authentication - The clients should be able to authenticate themselves to the server.
    
    \item Freshness - The retrieved data should be from a current time frame, if no recent data is available from a client, no data for that client is retrieved.
    
    \item Data Availability - Old location data should only be accessible to the client itself.
    
    \item Anonymity - Location information regarding other clients, not in your personal group, should only be accessible in shape of a heat map with a cut-off threshold, and pinpoint location should be inaccessible.
\end{itemize}


